### 2022-05-17 Publish Paper/manuscript_main.tex
Update publish paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main Text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{ACKNOWLEDGMENT} \\ 
I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung() who gave me the golden support to do this wonderful project. He gave a chance to use High GPU computing computer for AI Training. Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.  
\section{Introduction}
%The Need of AI-enabled computer-aided diagnostics
Skin cancer is one of the most common cancer leading causes of death worldwide. Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer. Otherwise, 3.6\cite{03358} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase\cite{11872}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99\%. However, once disease progresses beyond the skin, survival is poor\cite{11872}. Moreover, with the increasing
incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need of effective solution. \newline
%The Need of AI-enabled computer-aided diagnostics in Skin Lesion Clasification
Recently, deep learning particularly, and machine learning in generally algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis and Medical Treatment. Medical imaging, including ultrasound, computed tomography, and magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosed results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history medical data. In Medical Treatment, AI models are applied for building solution for a specific disease, medicine revolutionize is an example. In various studies, AI algorithms has provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}. \\
%The Success in AI - especially in CNN - some model based CNN
In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. Some of these models have been used as a backbone model in other studies that I will discuss more in the Related Work section. \\
In this paper, I will analyze the effect of the metadata on classifying skin disease. On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has ability to classify in a balanced way between classes instead of well identifying the majority of classes.

\section{Related Work}

@@

\begin{center}

@@

\end{center}

@@

Applying Soft-Attention layer in deep learning is not a new approach. Soft-Attention have been used in various application: image caption generation in \cite{03044} and handwriting verification in \cite{202017} respectively. In skin lesion classification, Soft-Attention is used to increase the performance of the model as described in \cite{03358}. Soft-Attention has ability to ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights. The function below describe the flow of Soft-Attention module:

@@

In order to apply Soft-Attention, there are two main steps. Firstly, the input tensor is put in a grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map\cite{08513}. This feature map called $t \in R^{h \times w \times d}$ where $h, w, and d$ is the shape of tensor generate by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$. The output of this convolution is normalized using softmax function to generate K = 16 attention maps. These $16$ attention maps are aggregated to produce a weight function called $\alpha$. This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar. Finally, the out of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps. 

@@

\subsection{Backbone Model Architecture}
In this paper, the backbone models that have been used are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both test by the previous paper\cite{03358} with a great performance. Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated. Therefore, in this paper, I will analyze the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth. On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.  
\begin{center}
	\begin{tabular}{|c | c c c|} 
		\hline
		Model & Size(MB) & Parameters & Depth \\ 
		\hline
		Resnet50 & 98 & 25.6M & 107 \\ 
		\hline
		Resnet152 & 232 & 60.4M & 311 \\ 
		\hline
		DenseNet201 & 80 & 20.2M & 402 \\
		\hline
		InceptionResNetV2 & 215 & 55.9M & 449 \\
		\hline
		MobileNet & 16 & 4.3M & 55 \\ 
		\hline
		MobileNetV2 & 14 & 3.5M & 105 \\ 
		\hline
		MobileNetV3Small & Unknown & 2.5M & 88 \\ 
		\hline
		MobileNetV3Large & Unknown & 5.5M & 118 \\
		\hline
		NasnetMobile & 23 & 5.3M & 308 \\
		\hline
		NasnetLarge & 343 & 88.9M & 533 \\ 
		\hline
	\end{tabular}
\end{center}

@@

	\caption{Overall Model}

@@

All the model in this paper is trained with Adam Optimizer\cite{6980}. The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$. Otherwise, the epsilon argument of the optimizer is set to $0.1$. The performance of all model is presented in the figure below:

@@

\clearpage
\pagebreak

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main Text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{ACKNOWLEDGMENT} \\ 
I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung (dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project. He gave a chance to use High GPU computing computer for AI Training. Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.  
I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung(dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project. He gave me a chance to use High GPU computing computers for AI Training. Furthermore, he also gave me recommendations on how to implement experiments to make a good conclusion such as what I should focus on, what I need to investigate, and which metrics I should consider.  
\section{Introduction}
%The Need of AI-enabled computer-aided diagnostics
Skin cancer is one of the most common cancers leading to worldwide death. Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer. Otherwise, 3.6\cite{03358} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase\cite{11872}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99\%. However, once the disease progresses beyond the skin, survival is poor\cite{11872}. Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution. \newline
%The Need of AI-enabled computer-aided diagnostics in Skin Lesion Clasification
Recently, deep learning particularly, and machine learning in general algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis, and Medical Treatment. Medical imaging, including ultrasound, computed tomography, magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosis results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history and medical data. In Medical Treatment, AI models are applied to building solutions for a specific disease, medicine revolution is an example. In various studies, AI algorithms have provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}. \\
%The Success in AI - especially in CNN - some model based CNN
In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. Some of these models have been used as a backbone model in other studies that I will discuss more in the Related Work section. \\
In this paper, I will analyze the effect of metadata on classifying skin disease. On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.

\section{Literature Review}
Skin lesion classification is not a new area, since there are many great performance models constructed. One of the most cutting-edge technologies that have been used is Soft-Attention as stated in\cite{03358}. Soumyya and his team construct several models formed by the combination of a backbone model including DenseNet201\cite{06993}, InceptionResNetV2\cite{00567}, ResNet50\cite{03385}\cite{05027}, VGG16\cite{1556} and Soft-Attention layer. Using those above backbones has been tried by many previous papers including \cite{03798} which uses transfer learning approach with CNN based model, \cite{10348} which does not only use those above backbone model but also used InceptionV3\cite{00567} model. Another paper that uses the backbone models is \cite{09418}. Hemanth and his team decide to use EfficientNet\cite{11946} and SeNET\cite{01507} instead and CutOut\cite{04552v2} method which involves creating
holes of different sizes on the images i.e. technically making a random portion of image inactive during data augmentation process. \cite{01284} also used Deep Convolution Neural Network. However, that paper used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative
Learning Strategy which can more effectively balance representation learning and
classifier learning without additional computational cost. Another state of the art is GradCam and Kernel SHAP\cite{06612}, which are both model agnostic, local interpretability methods that can highlight pixels that the trained network deems
relevant for the final classification.\\
Otherwise, the Student and Teacher Model is also a state of the art in 2021\cite{03225}. The student and teacher model is the combination of two-mode which share the memory with each other. Therefore, they can take full advantage of what others learn. SkinLinkNet\cite{12602} and WonderM\cite{03426} are both tested the effect of segmentation on skin lesion classification problem. Another approach is using metadata including gender, age, and capturing position as stated in \cite{03910}. \\
On the other hand, skin lesion classification problems are not only applied by Deep Learning but also Machine Learning. Random Forest, XGBoost, and Support Vector Machines are tested by \cite{03798}. Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in\cite{10348}. Matrix Transformation, besides is also applied before the soft-max activation function in \cite{05045}. 

@@

\begin{table}

@@

	\caption{Data Distribution in HAM10000}
	\label{table:1}
\end{table}

@@

Applying the Soft-Attention layer in deep learning is not a new approach. Soft-Attention has been used in various applications: image caption generation in \cite{03044} and handwriting verification in \cite{202017} respectively. In skin lesion classification, Soft-Attention is used to increase the performance of the model as described in \cite{03358}. Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights. The function below describes the flow of the Soft-Attention module:

@@

In order to apply Soft-Attention, there are two main steps. Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map\cite{08513}. This feature map called $t \in R^{h \times w \times d}$ where $h, w, and d$ is the shape of tensor generated by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$. The output of this convolution is normalized using the softmax function to generate K = 16 attention maps. These $16$ attention maps are aggregated to produce a weight function called $\alpha$. This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar. Finally, the out of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps. 

@@

\subsection{Backbone Model Architecture}
In this paper, the backbone models that have been used are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper\cite{03358} with a great performance. Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated. Therefore, in this paper, I will analyze the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth. On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.  
\begin{table}
	\centering
	\begin{tabular}{|c | c c c|} 
		\hline
		Model & Size(MB) & Parameters & Depth \\ 
		\hline
		Resnet50 & 98 & 25.6M & 107 \\ 
		\hline
		Resnet152 & 232 & 60.4M & 311 \\ 
		\hline
		DenseNet201 & 80 & 20.2M & 402 \\
		\hline
		InceptionResNetV2 & 215 & 55.9M & 449 \\
		\hline
		MobileNet & 16 & 4.3M & 55 \\ 
		\hline
		MobileNetV2 & 14 & 3.5M & 105 \\ 
		\hline
		MobileNetV3Small & Unknown & 2.5M & 88 \\ 
		\hline
		MobileNetV3Large & Unknown & 5.5M & 118 \\
		\hline
		NasnetMobile & 23 & 5.3M & 308 \\
		\hline
		NasnetLarge & 343 & 88.9M & 533 \\ 
		\hline
	\end{tabular}
\caption{Size and Parameters and Depth of backbone model used in this paper}
\label{table:2}
\end{table}

@@

	\caption{Overall Model Architecture}

@@

All the model in this paper is trained with Adam Optimizer\cite{6980}. The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$. Otherwise, the epsilon argument of the optimizer is set to $0.1$. The accuracy of all model is presented in the figure below:\\
\begin{table}[h]
	\begin{tabular}{| c | c | c | c |}
		InceptionResNetV2 & DenseNet201 & ResNet50 & VGG16 \\
		0.93 & 0.91 & 0.92 & 0.88\\
\caption{Accuracy of the model with augmented data}
\label{table:3}
\end{table}
\begin{table}[h]
	\begin{tabular}{| c | c | c | c | c |}
		InceptionResNetV2 & DenseNet201 & ResNet50 & Resnet152 & MobileNetV2\\
		0.89 & 0.89 & 0.70 & 0.57 & 0.81\\
\end{table}
\begin{table}[h]
	\begin{tabular}{| c | c | c | c |}
		MobileNetV3Large & MobileNetV3Small & NasNetLarge & NasNetMobile\\
		0.84 & 0.78 & 0.86 & 0.86\\
\caption{Accuracy of the model with metadata}
\label{table:4}
\end{table}\\
According to the Table 3 and 4, it is clear that the model trained with augmented data has a higher accuracy than the model trained with metadata only.  While InceptionResNetV2 and DenseNet201 trained with augmented data have accuracy of $0.93$ and $0.91$ respectively, their training with metadata has both the accuracy of $0.89$. Furthermore, Resnet50 trained with augmented data has the accuracy that outperform the Resnet50 and is twice as high as Resnet152 trained with metadata. On the other hand, mobile model including MobileNetV2, MobileNetV3Large, and NasNetMobile, although has a much smaller number of parameters and depth than the other model, they have a quite good accuracy of $0.81$, $0.84$, $0.86$, respectively. This term will be discussed later on. Although, the model trained with augmented data have high accuracy, when I analyzed the f1-score and the recall score of models, it turns out that models trained with augmented data have imbalanced f1-scores according to table 5. As a results, augmented data model dose not classify well on all class as InceptionRtesNetV2 trained on augmented data have 0.29 f1-score on class df while InceptionRtesNetV2 trained on metadata can classify well by a balanced way. This may cause by the augmented data. \\
However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class. The others still face the
the imbalanced term. Since this dataset is not balanced, therefore using augmented data can make the model bias to the class which has large sample. Using the metadata instead make the model less bias, though it still make the model imbalanced due to the high variance of model which has the number of depth much less than 400.\\ 
This problem is also true with the recall score according to table 6. DenseNet201, InceptionResNetV2, ResNet50, VGG16 trained with augmented data has recall standard deviation of $0.189$, $0.275$, $0.209$, $0.191$, respectively. On the other hand, other models have recall standard deviation which is close to $0.1$. Especially, inceptionResnetV2 train on metadata has recall standard deviation of approximately $0.09$. \\
As the results, metadata does not make the model more balanced and improve the model performance. The reason why the model become much more balanced is the weighted loss function. Weight loss function has ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class. Therefore, DenseNet201, InceptionResNetV2 trained with weighted loss function have recall in akiec of $0.85$. $0.82$, respectively, as opposed to their training in akiec without weighted loss function. MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile whose standard deviation is less than $0.15$ outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately. 
\begin{table}[h]
	\begin{tabular}{|l | c | c | c | c | c | c | c | c|} 
		Model & akiec & bcc & bkl & df & mel & nv & vasc & $\sigma$ \\
		DenseNet201 + Augmented Data & 0.67 & 0.78 & 0.64 & 0.67 & 0.61 & 0.96 & 0.91 & 0.128 \\ 
		InceptionResNetV2 + Augmented Data & 0.69 &	0.88 & 0.77 & 0.29 & 0.66 & 0.98 & 1 & 0.225\\
		Resnet50 + Augmented Data & 0.53 & 0.86 & 0.68 & 0.67 & 0.57 & 0.97 & 0.95 & 0.165\\
		VGG16 + Augmented Data & 0.65 & 0.7 & 0.52 & 0.4 & 0.53 & 0.95 & 0.95 & 0.197\\ 
		DenseNet201 + Metadata & \textbf{0.84} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.088}\\
		InceptionResNetV2 + Metadata & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.09}\\
		Resnet50 + Metadata & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.162\\
		Resnet152 + Metadata & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.199\\
		MobileNetV2 + Metadata & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & 0.9 & 0.122\\
		MobileNetV3Large + Metadata & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & 0.92 & 0.12\\
		MobileNetV3Small + Metadata & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & 0.89 & 0.144\\
		NasNetLarge + Metadata & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.088}\\
		NasNetMobile + Metadata & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & 0.93 & 0.101\\
	\caption{F1-Score of each class and the standard deviation of each model}
	\label{table:5}
\end{table}\\
\begin{table}[h]
	\begin{tabular}{|l | c | c | c | c | c | c | c | c|} 
		Model & akiec & bcc & bkl & df & mel & nv & vasc & $\sigma$ \\
		DenseNet201 + Augmented Data & 0.52 & 0.77 & 0.58 & 0.5 & 0.71 & 0.97 & 1 & \textbf{0.189}\\ 
		InceptionResNetV2 + Augmented Data & 0.52 & 0.88 & 0.83 & 0.17 & 0.65 & 0.98 & 1 & \textbf{0.275}\\
		Resnet50 + Augmented Data & 0.43 & 0.85 & 0.7 & 0.5 & 0.47 & 0.98 & 0.9 & \textbf{0.209}\\
		VGG16 + Augmented Data & 0.61 & 0.81 & 0.44 & 0.44 & 0.68 & 0.95 & 0.9 & 	\textbf{0.191}\\ 
		DenseNet201 + Metadata & \textbf{0.85} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & 0.116\\
		InceptionResNetV2 + Metadata & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 	0.93 & \textbf{0.097}\\
		Resnet50 + Metadata & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.107\\
		Resnet152 + Metadata & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.121\\
		MobileNetV2 + Metadata & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.126\\
		MobileNetV3Large + Metadata & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & 0.12\\
		MobileNetV3Small + Metadata & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.147\\
		NasNetLarge + Metadata & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & 0.119\\
		NasNetMobile + Metadata & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & 0.134\\
	\caption{Recall score of each class and the standard deviation of each model}
	\label{table:6}
\end{table}\\
\begin{table}[h]
	\begin{tabular}{|l | c | c | c | c | c | c | c|} 
		Model & akiec & bcc & bkl & df & mel & nv & vasc \\
		DenseNet201 + Augmented Data & 0.96 & 0.98 & 0.9 & 0.80 & 0.95 & 0.95 & 0.999\\ 
		InceptionResNetV2 + Augmented Data & 0.96 & 0.99 & 0.96 & 0.92 & 0.97 & 0.976 & 0.999\\
		Resnet50 + Augmented Data & 0.97 & 0.99 & 0.91 & 0.94 & 0.95 & 0.95 & 0.99\\
		VGG16 + Augmented Data & 0.98 & 0.99 & 0.96 & 0.97 & 0.97 & 0.97 & 0.99\\ 
		DenseNet201 + Metadata & 0.99 & 0.99 & 0.97 & 0.99 & 0.92 & 0.96 & 0.99\\
		InceptionResNetV2 + Metadata & 0.98 & 0.98 & 0.98 & 0.98 & 0.95 & 0.96 & 0.99\\
		Resnet50 + Metadata & 0.97 & 0.95 & 0.88 & 0.99 & 0.85 & 0.92 & 0.98\\
		Resnet152 + Metadata & 0.95 & 0.9 & 0.84 & 0.92 & 0.82 & 0.89 & 0.8\\
		MobileNetV2 + Metadata & 0.97 & 0.98 & 0.94 & 0.99 & 0.9 & 0.95 & 0.99\\
		MobileNetV3Large + Metadata & 0.99 & 0.98 & 0.96 & 0.99 & 0.92 & 0.95 & 0.99\\
		MobileNetV3Small + Metadata & 0.97 & 0.97 & 0.93 & 0.99 & 0.87 & 0.94 & 0.99\\
		NasNetLarge + Metadata & 0.95 & 0.98 & 0.97 & 1 & 0.92 & 0.95 & 1\\
		NasNetMobile + Metadata & 0.98 & 0.99 & 0.97 & 1 & 0.9 & 0.96 & 1\\
	\caption{ROC AUC Score of each model}
	\label{table:7}
\end{table}\\
Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance. The table 8 illustrates the deeper analyzing of the three models.\\
\begin{table}
	\begin{tabular}{l | c | c | c | c|}
		Model & MobileNetV2 & MobileNetV3Smal & MobileNetV3Large & NasNetMobile\\
		Accuracy(avg)\\
		Balanced Accuracy(avg)\\ 
		Precision(avg)\\
		F1-score(avg)\\
		Sensitivity(avg)\\ 
		Specificity(avg)\\
		ROC-AUC-score(avg)\\
\end{table}

@@

\clearpage
\pagebreak
